### 2012-02-11 trunk/GUIErrorDetector/paper/evaluation.tex
spell checks

\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox}  allows users
to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions efficiently using mutlithreaded execution.

@@

The second variant uses DFS for graph traversal by changing
the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
a stack, and changing queue operations (\CodeIn{dequeue} and \CodeIn{enqueueAll}
on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
to the corresponding statck operations (\CodeIn{pop} and \CodeIn{pushAll}).
This variant found 11 errors in total and missed 1 error in the FileBunker subject.
The reason is that DFS tends to search deeper into the graph, and the path it returns
may not be the shortest one and is more likely to be an infeasible path in practice.
%For the FileBunker subject, paths
%returned by DFS are much longer than BFS, and do not actually exist.

@@

\noindent \textbf{\textit{Performance and scalability.}} Our tool
has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
with 1.4 MLOC, showing good scalability. Our evaluations
were conducted on a 2.67GHz Intel Core PC with 4GB
physical memory (1GB is allocated for JVM), running Fedora 16.
For the most time-consuming subject, MyTracks, our tool finished the whole analysis
within 209 seconds using the most expensive call graph construction
algorithm: the reflection-aware 1-CFA algorithm. Analyzing
other subjects using different algorithms took less time.
The performance has not been tuned, and we believe
that it could be improved further.

>>>>

\Item \textbf{Swing applications.} %S3dropbox~\cite{s3dropbox} and SudokuSolver~\cite{sudokusolver} are two Swing desktop applications.
S3dropbox~\cite{s3dropbox}  allows users
to drag and drop files to their Amazon S3 accounts. SudokuSolver~\cite{sudokusolver}
computes Sudoku solutions using mutlithreaded execution.

@@

The second variant uses DFS for graph traversal by changing
the data structure of $\mathit{worklist}$ on line 7 in Figure~\ref{fig:detectalgorithm} to
a stack, and changing queue operations (\CodeIn{dequeue} and \CodeIn{enqueueAll}
on lines 10 and 21 in Figure~\ref{fig:detectalgorithm}, respectively)
to the corresponding stack operations (\CodeIn{pop} and \CodeIn{pushAll}).
This variant found 11 errors in total and missed 1 error in the FileBunker subject.
The reason is that DFS tends to search deeper into the graph, and the path it returns
may not be the shortest one and is more likely to be an infeasible path in practice.
%For the FileBunker subject, paths
%returned by DFS are much longer than BFS, and do not actually exist.

@@

\noindent \textbf{\textit{Performance and scalability.}} Our tool
has been evaluated on \subnum subjects with over \totaloc LOC and frameworks
with 1.4 MLOC, showing good scalability. Our evaluations
were conducted on a 2.67GHz Intel Core PC with 4GB
physical memory (1GB is allocated for JVM), running Fedora 16.
For the most time-consuming subject, S3dropbox, our tool finished the whole analysis
within 252 seconds using the most expensive 1-CFA call graph construction
algorithm. Analyzing other subjects using different algorithms took less time.
The percentage of call graph construction cost ranges
from 33.4\% (Fennec) to 91.1\% (VirgoFTP) out of
the total analysis time among all evaluated programs.
%The performance has not been tuned, and we believe
%that it could be improved further.

### 2012-02-11 trunk/GUIErrorDetector/paper/introduction.tex
spell checks

Stylized coding patterns are also inadequate. One possible rule is to always
access GUI objects via asynchronous message passing, to ensure a GUI object is accessed in
the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror}
by wrapping line 222 inside a \CodeIn{post} message-passing method\footnote{The
\CodeIn{post} method in class \CodeIn{android.widget.View} is a
a standard way to send asynchronized messages to the UI-thread.}, as follows:

@@

Such an approach is desirable for accesses from non-UI threads, but it is unnecessary.
In our evaluation on real-world programs, we found a simple analysis that
requires GUI operations to be in a message issued
an unacceptable number of warnings. %false positives and redundant warnings.
Furthermore, this approach is dangerous for accesses from the UI thread. Asynchronized message passing offers
no timing guarantee, so a GUI object may have already been
disposed before the message sent to it arrives, causing other bugs.

>>>>

Stylized coding patterns are also inadequate. One possible rule is to always
access GUI objects via asynchronous message passing, to ensure a GUI object is accessed in
the UI thread. For example, a developer could have prevented the bug in Figure~\ref{fig:androiderror}
by wrapping line 222 inside a \CodeIn{post} message-passing method\footnote{The
\CodeIn{post} method in class \CodeIn{android.widget.View} is
a standard way to send asynchronous messages to the UI-thread.}, as follows:

@@

Such an approach is desirable for accesses from non-UI threads, but it is unnecessary.
In our evaluation on real-world programs, we found that a simple analysis that
requires GUI operations to be in a message issued
an unacceptable number of warnings. %false positives and redundant warnings.
Furthermore, this approach is dangerous for accesses from the UI thread. Asynchronized message passing offers
no timing guarantee, so a GUI object may have already been
disposed before the message sent to it arrives, causing other bugs.
